Analysing Constraint Grammar with a SAT solver

### 2015-10-16 paper/lrec/implementation.tex
make table nicer

\begin{table*}[]
\centering
\caption{SAT-encoding of CG}
\label{table:vars}
\begin{tabular}{|l|p{1.9cm}|l|l|}
\hline
\textbf{Word} & \textbf{Variables} & \textbf{Default rules} & \textbf{Constraint rules}\\ \hline
\multirow{2}{*} ``the''  & \texttt{the\_det}  & \texttt{the\_det} & {\texttt{the\_det} $\Rightarrow$ $\neg$\texttt{bear\_v\_pl}} \\
                ``bear'' & \texttt{bear\_n\_sg}  \texttt{bear\_v\_pl} & \texttt{bear\_n\_sg} $\vee$ \texttt{bear\_v\_pl} & \\  \hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[]
\centering
\caption{SAT-encoding of \texttt{REMOVE v IF (-1 det)} applied to \emph{the bear}}
\label{table:vars}
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Word} & \textbf{Variables}                                                          & \textbf{Default rules}               & \textbf{Constraint rules}                                  \\ \hline
``the''         & \texttt{the\_det}                                                           & \texttt{the\_det}                    & \multirow{2}{*}{\texttt{the\_det}  $\Rightarrow$ $\neg$\texttt{bear\_v\_pl}} \\ \cline{1-3}
``bear''        & \begin{tabular}[c]{@{}l@{}}\texttt{bear\_n\_sg} \\ \texttt{bear\_v\_pl}\end{tabular} & \texttt{bear\_n\_sg} $\vee$ \texttt{bear\_v\_pl} &                                                            \\ \hline
\end{tabular}
\end{table*}
